---
title: "Map of Ground-based Astronomical Observatories"
author: "Wayne Heller"
date: "July 7, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This interactive map was created as part of the Johns Hopkins Coursera Data Science Specializaiton Course - Developing Data Products.  

The information on this map was scraped from the Wikipedia page https://en.wikipedia.org/wiki/List_of_astronomical_observatories The webscraping code is located here: https://github.com/wayneheller/developingdataproducts/blob/gh-pages/scrapeObservatoryInfo.R and at the time of this writing is still being refined.

The instructions for this course assignment are fairly broad:  

**Create a web page using R Markdown that features a map created with Leaflet.**  

*Host your webpage on either GitHub Pages, RPubs, or NeoCities.*  

*Your webpage must contain the date that you created the document, and it must contain a map created with Leaflet. We would love to see you show off your creativity!*

**Review criteria**

*The rubric contains the following two questions:*

*Does the web page feature a date and is this date less than two months before the date that you're grading this assignment?*

*Does the web page feature an interactive map that appears to have been created with Leaflet?*


## Interactive Map of Ground-based Astronomical Observatories


```{r leaflet_map, echo=FALSE,}
suppressWarnings(library(leaflet))



makeHref <-function(url, lnk) {
        wikipediaUrl <- "http://en.wikipedia.org"
        href <- paste0("<a href='", wikipediaUrl, url, "'>", lnk, "</a>")
        return(href)
}
dfObservatories <- read.csv("observatories.csv")
my_map <- leaflet() %>% addTiles()
my_map <- my_map %>% addMarkers(lat=dfObservatories$latitude, lng=dfObservatories$longitude,
                                popup=apply(dfObservatories[,c('url','link')], 1, function(x) makeHref(x[1],x[2])),
                                clusterOptions = markerClusterOptions())
        
my_map
```


